Clustering Beat-Chroma Patterns\\ in a Large Music Database

### 2010-03-24 Paper/Paper.tex
improved
reworded section 5.2

\section{Applications}\label{sec:exps2}
In this section we describe two other applications of the clustering
described in this paper: the song segmentation, and artist
recognition.  This demonstrates the utility of unsupervised clustering
to FIXME ... 
% Although our algorithm was not devised for any of these
% tasks, but some information contained in the centroids can be
% naturally used.

\subsection{Song Segmentation} \label{ssec:segment}
We explained that we used bars as defined by the EchoNest algorithm to
train our patterns. Let's assume once again that those bars are
reasonable. We investigate whether we could recover the bar segmentation
of new songs from our codebook. It would helps us assert that codes
encodes something related to bars, for instance a strong beat at the
beginning. Results are shown \ref{tab:offset}. We find the right segment
with an accuracy of $62\%$ where random is $25\%$. Details of the
experiment follow.

We train a codebook of size $100$ on bars resized to $4$ beats. Then,
we take the longest sequence of bars of $4$ beats in the test set.
As we mentioned before, $4$ beats is the most common (by far!) bar size
in terms of beats according to the EchoNest API. We then encode this
sequence using an offset of $0$, $1$, $2$ or $3$ beats. The best offset
is the one that gives the encoding with the lowest distortion. The
good answer is an offset of $0$.

>>>>

\section{Applications}\label{sec:exps2}
In this section we describe two other applications of the clustering
described in this paper: song segmentation, and artist
recognition.  This demonstrates the utility of unsupervised clustering
to FIXME ... 
% Although our algorithm was not devised for any of these
% tasks, but some information contained in the centroids can be
% naturally used.

\subsection{Song Segmentation} \label{ssec:segment}

Since the clustering described in Section \ref{sec:approach} is based
on the segmentation of the signal in to bars, it stands to reason that
the cluster centroids should contain information related to bar
alignment, such as the presence of a strong beat on the first beat.
%
In this section we investigate whether it is possible to recover the
bar segmentation of new songs using the information contained in the
cluster centroids.  The results are shown \ref{tab:offset}. We find
the right segment with an accuracy of $62\%$ where random is
$25\%$. Details of the experiment follow.

We train a codebook of size $100$ on bars resized to $4$ beats. Then,
we take the longest sequence of bars of $4$ beats in the test set.  As
we mentioned before, $4$ beats is the most common bar size using the
Echo Nest segmentation. We then encode this sequence using an offset
of $0$, $1$, $2$ or $3$ beats. The best offset in terms of distortion
should correspond to the bar alignment relative to the original
feature matrix.

FIXME: Actually I'm (ronw) not sure how this was done.  Every 4 beat
segment was treated separately?  Its not looking for a per-song alignment?
%The good answer is an offset of $0$.
